---
title: "CAR PRICE PREDICTION"
author: "yuvaraj"
date: "10/08/2021"
output: html_document
---


```{r}
library(tidyverse)
library(DescTools)
```
load the file
```{r}
library(readr)
geely=read.csv("D:/3sem project/CarPrice_Assignment.csv")
geely

```

```{r}
attach(geely)
```

```{r}
??geely
```
						
1	Car_ID			     Unique id of each observation (Interger)		
2	Symboling 			 Its assigned insurance risk rating, A value of +3 indicates that the auto is                         risky,  -3 that it is probably pretty safe.(Categorical) 		
3	carCompany			 Name of car company (Categorical)		
4	fueltype		   	 Car fuel type i.e gas or diesel (Categorical)		
5	aspiration			 Aspiration used in a car (Categorical)		
6	doornumber			 Number of doors in a car (Categorical)		
7	carbody			     body of car (Categorical)		
8	drivewheel			 type of drive wheel (Categorical)		
9	enginelocation	 Location of car engine (Categorical)		
10	wheelbase			 Weelbase of car (Numeric)		
11	carlength			 Length of car (Numeric)		
12	carwidth			 Width of car (Numeric)		
13	carheight			 height of car (Numeric)		
14	curbweight		 The weight of a car without occupants or baggage. (Numeric)		
15	enginetype		 Type of engine. (Categorical)		
16	cylindernumber cylinder placed in the car (Categorical)		
17	enginesize		 Size of car (Numeric)		
18	fuelsystem		 Fuel system of car (Categorical)		
19	boreratio			 Boreratio of car (Numeric)		
20	stroke			   Stroke or volume inside the engine (Numeric)		
21	compression
    ratio			     compression ratio of car (Numeric)		
22	horsepower		 Horsepower (Numeric)		
23	peakrpm			   car peak rpm (Numeric)		
24	citympg			   Mileage in city (Numeric)		
25	highwaympg		 Mileage on highway (Numeric)		
26	price(Dependent 
     variable)	   Price of car (Numeric)		
     
```{r}
library(Hmisc)
describe(geely)
```
     

```{r}
view(geely)

```

```{r}
summary(geely)
```
```{r}
str(geely)
```
```{r}
dim(geely)
```
```{r}
nrow(geely)
ncol(geely)
```

```{r}
names(geely)
```


```{r}
summary(geely)
```

```{r}
colSums(is.na(geely))

```

```{r}
table(fueltype)
```
```{r}
table(aspiration)
```
```{r}
table(doornumber)
```
```{r}
table(carbody)
```
```{r}
table(drivewheel)
```
```{r}
table(enginelocation)
```
```{r}
table(enginetype)
```
```{r}
table(cylindernumber)
```

```{r}
table(fuelsystem)
```
```{r}
library(tidyverse)
library(tidyr)
geely=separate(geely,CarName,into=c("company_name","model"),sep=" ")


```

```{r}

company_name=as.factor(geely$company_name)
```
 
```{r}
names(geely)
```


```{r}
table(company_name)
```
```{r}
geely<-geely%>%mutate(model = ifelse(is.na(model), "Not_available",geely$model))
geely

```
 
```{r}
geely$model          =as.factor(geely$model)
geely$fueltype       = as.factor(geely$fueltype)
geely$aspiration     = as.factor(geely$aspiration)
geely$doornumber     = as.factor(geely$doornumber)
geely$carbody        = as.factor(geely$carbody)
geely$drivewheel     = as.factor(geely$drivewheel)
geely$enginelocation = as.factor(geely$enginelocation)
geely$enginetype     = as.factor(geely$enginetype)
geely$cylindernumber = as.factor(geely$cylindernumber)
geely$fuelsystem     =as.factor(geely$fuelsystem)


```



```{r}
geely$company_name[which(geely$company_name=="toyouta")]="toyota"
geely$company_name[which(geely$company_name=="vokswagen")]="volkswagen"
geely$company_name[which(geely$company_name=="vw")]="volkswagen"
geely$company_name[which(geely$company_name=="Nissan")]="nissan"
geely$company_name[which(geely$company_name=="maxda")]="mazda"
geely$company_name[which(geely$company_name=="porcshce")]="porsche"
```

```{r}
str(geely)
```
```{r}
summary(geely)
```


// Perform EDA

relationship bw 2  variables
```{r}
library(ggplot2)
```

//geom boxplot
```{r}
ggplot(geely,mapping=aes(fueltype,price))+geom_boxplot()
```


// Line Chart
```{r}
ggplot(geely,mapping=aes(horsepower,price,col=geely$fueltype))+geom_line()
```


//histogram
```{r}
ggplot(geely)+geom_histogram(mapping=aes(fill=enginetype,price),Position = "dodge")
```

//point with line chart
```{r}
library(tidyverse)
```

```{r}
geely%>%filter(highwaympg>30)%>%ggplot(mapping=aes(horsepower,price,col=fueltype))+geom_line()+geom_point()
```
```{r}
geely%>%filter()%>%ggplot(mapping=aes(horsepower,price,col=drivewheel))+geom_line()+geom_point()
```
###model building
```{r}
geely$model[is.na(geely$model)]<-mean(geely$model,na.rm=TRUE)
geely
```


```{r}
train1=sample(nrow(geely),nrow(geely)*0.9)
train=geely[train1,]
test=geely[-train1,]
```


```{r}
library(tree)
```

```{r}
tree_fit=tree(price~.,data=train)
tree_fit
summary(tree_fit)
```

```{r}
plot(tree_fit)
text(tree_fit,pretty=0)

```

```{r}
cv_gly=cv.tree(tree_fit)
cv_gly
```

```{r}
names(cv_gly)
```

```{r}
plot(cv_gly$size,cv_gly$dev,type = "b")
```


```{r}
prune_gly=prune.tree(tree_fit,best=3)
plot(prune_gly)
text(prune_gly,pretty=0)
```

```{r}
tr_predict=predict(tree_fit,newdata=test)
tr_predict
```



```{r}
plot(tr_predict,test$price)
abline(0,1)

```

```{r}
mean((tr_predict-test$price)^2)
```

###random forest

```{r}

library(randomForest)
```

```{r}
sqrt(26)
set.seed(1)
rfm=randomForest(train$price ~.,data=train,mtry=6,ntree=500,importance=TRUE)
summary(rfm)
```

```{r}
plot(rfm)
```

```{r}
predict_rfm= predict(rfm, newdata=test)
predict_rfm
```

```{r}
plot(predict_rfm,test$price)
abline (0,1)

```

```{r}
mean((predict_rfm-test$price)^2)
```


